---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LeeDiD

<!-- badges: start -->
[![R-CMD-check](https://github.com/JavierViviens/claude-code-my-workflow/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JavierViviens/claude-code-my-workflow/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://img.shields.io/badge/CRAN-not%20yet%20submitted-lightgrey)](https://cran.r-project.org/)
<!-- badges: end -->

LeeDiD implements the identification and estimation strategy of Viviens
(2026), *“Estimating the Intensive Margin Effect in Panel Data
Settings,”* for recovering the **intensive margin treatment effect**
(e.g., the effect on those always observed, regardless of the treatment received) in panel data when
treatment is not randomly assigned.

The package adapts the Horowitz-Manski-Lee bounds to both the canonical Difference-in-Differences and the
Changes-in-Changes frameworks to partially identify the average and
quantile treatment effect on the treated among **“Always Observed”
(AO)** units — those who would be selected into the estimation sample
under either treatment arm. Unlike the original Lee bounds,
identification here draws on **multiple sources of sample selection
jointly** (e.g., employment status *and* survey attrition), which
relaxes the monotonicity assumption in the original Lee bounds.

## Installation

LeeDiD is not yet on CRAN. Install the development version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("JavierViviens/claude-code-my-workflow", subdir = "LeeDiD")
```

## Example

```{r example}
library(LeeDiD)

data(leedid_sim)

fit <- leedid(
  data           = leedid_sim,
  yname          = "y",
  tname          = "time",
  idname         = "id",
  gname          = "group",
  selection_vars = c("employed", "responded"),
  t              = 2,
  tmin1          = 1,
  boot           = TRUE,
  biters         = 199,
  seed           = 1
)

fit
```

```{r plot-example}
plot(fit)
```

## Learn more

See `vignette("intro-to-leedid")` for a full walkthrough of the method and
the package's API.
