---
title: "Introduction to LeeDiD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to LeeDiD}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LeeDiD)
```

## The problem

Many policies operate through two channels: an **extensive margin** (whether
a unit participates at all) and an **intensive margin** (how intensely
participants respond). A canonical example is a job-training program that
affects both the probability of employment and, among the employed, wages.
Recovering the intensive margin effect is complicated when the very fact of
being observed (e.g., being employed, or responding to a follow-up survey)
is itself affected by treatment and correlated with the outcome.

LeeDiD implements the identification and estimation strategy of Viviens
(2026) for this setting: it adapts the Horowitz-Manski-Lee bounds to the
Changes-in-Changes (CiC) framework to partially identify the average and
quantile treatment effect on the treated among **"Always Observed" (AO)**
units — those who would have been selected into the estimation sample under
*either* treatment arm. Unlike the original Lee bounds, which require a
single source of sample selection satisfying a monotonicity assumption,
this approach uses **multiple sources of sample selection jointly** (e.g.,
employment status *and* survey response), which relaxes that assumption.

## The data

`leedid()` expects a balanced two-period panel: exactly one pre-treatment
and one post-treatment row per unit, a time-invariant 0/1 group assignment,
an outcome that is `NA` whenever a unit is not selected in a given period,
and two or more 0/1 columns marking each source of selection.

```{r}
data(leedid_sim)
head(leedid_sim)
```

Here `group` is the (time-invariant) treatment assignment, and a unit's
outcome `y` is observed only when both `employed == 1` and
`responded == 1`.

## Estimating the intensive margin effect

```{r}
fit <- leedid(
  leedid_sim,
  yname          = "y",
  tname          = "time",
  idname         = "id",
  gname          = "group",
  selection_vars = c("employed", "responded"),
  t              = 2,
  tmin1          = 1,
  boot           = TRUE,
  biters         = 199,
  seed           = 1
)
fit
```

The printed summary reports the estimated AO shares (`pi_0`, `pi_1`), the
unconditional CiC point estimate of the ATT, the partially identified AO
bounds on the ATT with their bootstrap standard error and Imbens-Manski
(2004) confidence interval, and the classical two-way fixed-effects DiD
estimate (with its own AO-trimmed bounds) as a benchmark comparison.

## Quantile effects

`summary()` additionally reports the bounds on the quantile treatment
effect on the treated across a grid of quantiles:

```{r}
summary(fit)
```

`plot()` visualizes the same bounds:

```{r plot-fit, fig.width=6, fig.height=4}
plot(fit)
```

## Individual building blocks

The pieces of the pipeline are also available on their own, useful for
diagnostics or for building alternative aggregation schemes (e.g., across
covariate strata):

- `compute_ao_share()` — estimate `pi_0`/`pi_1` from the selection sources
- `empirical_cdfs()` — the four group/period empirical CDFs and the CiC
  counterfactual
- `cic_qtt()` / `cic_bounds()` — the unconditional QTT and its AO bounds
- `bootstrap_se()` — bootstrap standard errors for all of the above
- `imbens_manski_ci()` — confidence interval for a partially identified
  parameter, given estimates and standard errors of its bounds

## A note on this release

The real-data application in Viviens (2026) uses a Colombian job-training
survey (Attanasio, Kugler and Meghir); that dataset is third-party and is
not yet redistributed with this package pending confirmation of the
applicable data-sharing terms. `leedid_sim` is a simulated dataset (see
`?leedid_sim`) used here purely to illustrate the package's interface.
